---
title: "Covid91 vaccine study Final2024"
author: "Kelly Acevedo"
output: 
  html_document:
    number_sections: true
    toc: true
    toc_depth: 5
date: 04/25/24 
---

```{r include=FALSE,echo=FALSE}
require(tidyverse)
require(tigerstats)
require(forcats)
FinalDat <-read.csv(file="final.csv",header=TRUE)
#recode to remove the annoying "X" from the dataframe
FinalData <- FinalDat  %>% select(-one_of("X"))
FinalData <- FinalData %>%
mutate(across(where(is.character), as.factor))
male = filter(FinalData, sex =="M")
female = filter(FinalData, sex =="F")
lgbtq = filter(FinalData, LGBTQ =="gay")
drugUser = filter(FinalData, DrugUser =="yes")

```


# Introduction

A new  preventative vaccine (covid921) is under test in clinical trials. Given the nature of this vaccine it is suspected that the drug may exhibit different effectiveness across the variety of subpopulations tracked. Consider population subgroups by gender( guys and gals), drug use, and sexual orientation. Write a complete report that separately considers this drug for each subgroup and your recommendations as to whether people in the subgroup should take the vaccine. Structure your report in four sections each devoted to one of the four subgroups, use null and alternative hypothesis statements and correct statistical verbage when referencing p-values in conclusions.

## Males

```{r}
barchartGC(~infected + treatment,data=male)
barchartGC(~infected + treatment,data=male, type="percent")
```
```Based on the information shown in the graph we can say that there is a difference 30% with Covid and 70% with a placebo 
to those who received Covid.There is a small difference among those who received the vaccinations (ok).
##Numerical
```{r}
tableMale <- xtabs(~infected + treatment, data=male)
rowPerc(tableMale)
colPerc(tableMale)
```
```the data shows that  Effective on males in this group were  two times difference among those who received the vaccinations and experienced Covid and  70% of those who took the placebo didnt get it, compared to 30% of those who got the vaccination. There was not a noticeable distinction among those who received vaccinations and (ok).

##Inferential 
```{r}
chisq.test(tableMale)
chisqtestGC(tableMale)
maleFisher <- fisher.test(tableMale)
maleFisher
```
This shows that the vaccine is not effective in preventing Covid among males.P-valuse is 0.0000000000001098 which its too small that's why it failed to reject the null hypothesis.However according to the Fisher's Exact test the P-value is 0.00000000000004631 meaning there is a difference in getting Covid and being a male.so as a male, the chances of acquiring Covid are the same.




##Females
```{r}
barchartGC(~infected + treatment,data=female)
barchartGC(~infected + treatment,data=female, type="percent")
```

Based on the information we can say that those who received Covid there was a difference between 40% and 60% placebo among the females who received the vaccination. The Female who got the vaccination and were (ok) showed no difference.


## LGBTQ



## Druggies


# Overall Results and Conclusions

```{r}
tableMale <- xtabs(~infected + treatment, data=male)
rowPerc(tableMale)
colPerc(tableMale)
```

